Everest Bio

### 2021-04-12 slides/index.Rmd
final

```{r, out.width = '500px', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Everest-bio/Fedoua.jpg'))
```
]

>>>>

```{r, out.width = '500px', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Everest-bio/Fedoua.jpg'))
```

```{r, out.width = '500px', fig.align='center'}
knitr::include_graphics(paste0(URL, 'Everest-bio/Pavlo.jpg'))
```
